---
title: "Lab 02 - Plastic waste"
author: "YooRi"
date: "Insert date here"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
glimpse(plastic_waste)
View(plastic_waste)
```

## Exercises

warm up: NA=missing data

### Exercise 1

TTO is the highest on their plastic_waste_per_cap


```{r plastic-waste-continent}
ggplot(data=plastic_waste, aes(x=plastic_waste_per_cap))+
  geom_histogram(bindwidth=0.2)

ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_density()

plastic_waste %>%
  filter(plastic_waste_per_cap>3.5)%>%
  View()

ggplot(data=plastic_waste, aes(x=plastic_waste_per_cap))+
  geom_histogram(bindwidth=0.2)+
  facet_wrap(~continent)

ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent)) +
  geom_density()
  

ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha=0.5)
  
```

### Exercise 2

it can cover other graph in the back layer. 
so, if we can make somewhat transparent, we can see the back layer. 

```{r plastic-waste-density}

ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha=0.2)

ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_boxplot()

```

### Exercise 3

basic backgrounds on violin plot (since I saw this for the first time:D)

( if the following contains incorrect information, let me know plz..)

violin graph is symmetric, mirroring the estimation of Kernel Density Estimation (KDE)--to my understanding, it can be used to smooth the histogram. 

with this plot, we can visualize the range of data distribution--especially, more close to a real data distribution. 

box plot has more apparent in median, 1rd/3rd quantile

reference: R graphics cookbook, author = winston chang 

```{r}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()

# let's twist little more :D


ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green")+
  stat_summary(fun.y=median, geom="point")


```

### Exercise 4

it seems that it has positive relationship (4-1)
yea, it seems a little. (4-2)
not really (4-3)


```{r plastic-waste-violin}
#4-1
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     y = mismanaged_plastic_waste_per_cap))+
  geom_point()

#4-2
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     y = mismanaged_plastic_waste_per_cap,
                     color=continent))+
  geom_point() #+
  #stat_smooth(method=lm)

#4-3
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     y = total_pop))+
  geom_point()

ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     y = coastal_pop))+
  geom_point()

#4-3-2 XD
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     y = total_pop))+
  geom_point()+
  stat_smooth(method=lm)


ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     y = coastal_pop))+
  geom_point()+
  stat_smooth(method=lm)

```

### Exercise 5

change background color/grid line color of the plot
references:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements


```{r}
plastic_waste$cp_prop<-
  plastic_waste$coastal_pop/plastic_waste$total_pop

plastic_waste %>%
  filter(plastic_waste_per_cap<3)%>%
  ggplot(mapping = aes(x =cp_prop,
                     y = plastic_waste_per_cap,
                     ))+
  geom_point(aes(color=continent,))+
  stat_smooth(color="black")+
  scale_colour_viridis_d()+
  labs(title="plastic waste vs. coastal poplualtion portion",
       subtitle="by continent",
       x="Coastal population proportion(Coastal/total population)",
       y="Plastic waste per capita")+
  theme_minimal()


```


reference: R graphics cookbook, author = winston chang 